\documentclass{article}
\usepackage{hyperref}

\begin{document}

My task is to read "The twelve factor app" and answer the following.

\begin{itemize}
\item Research Internet sources discussing the recommendations.
\item Based on your findings, try to re-order(re-number) the know factors accordingly
\item be ready to argument these criteria in class
\end{itemize}

\section*{Research Internet sources discussing the recommendations.}

\subsection*{Dependencies}
This is a blog, where some cons against dependencies are found:
\begin{itemize}
\item \url{https://techblog.bozho.net/comments-on-the-twelve-factor-app/}
\end{itemize}
The idea mentioned here, is to avoid big app package, by have the app rely on something. I do think this will also affect the fast startup time covered by the Disposability step.
You cannot start up a new instance of the app on a new server, if this server has to have some form of tools on it.

\subsection*{all-round}
This is a blog, where the author takes all the step and grade the importance on a scale of 1-5
\begin{itemize}
\item \url{https://gaddings.io/comments-on-the-twelve-factor-app/}
\end {itemize}

\section*{Re-order the know factors}
To be honest, i can follow all the steps, and see them as equally important. I think the order is to be seem more of the order you would do all the task, to go from nothing to a fully running app.
I do believe of the step can be skipped if not needed, ie if the app does not need a log, this step can be skipped.

\section*{What is The twelve-factor app?}
The twelve-factor app, is a methodology for building Software-As-A-Service programs.

There are twelve step that has to be followed.


The step are:
\input{Codebase}
\input{Dependencies}
\input{Config}
\input{Backing}
\input{Build}
\input{Process}
\input{Port}
\input{Concurrency}
\input{Disposability}
\input{Dev}
\input{Logs}
\input{Admin}



\end{document}